---
title: "Experiment 3: Time_on_task"
output:
  html_document:
    df_print: paged
    toc: true
---

# Introduction

In a preregistered study we manipulated the influence of time on task (Self-paced vs. Timed (3 s) on the Sans Forgetica effect/disfluency effect. We collected 232 participants (116 in each group) on Prolific. This file explains how to read in the data, analyze, and plot the results. 

## Load in packages

```{r}
#packages you will need
library(tidyverse)
library(data.table)
library(here)
library(afex)
library(Rmisc)
library(cowplot)
library(patchwork)
library(see)
library(ggrepel)
library(report)

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R") # violin graph source code

```

## Read in Data

First we must read in data for each counterbalanced list. There were four and there was no simple way to counterbalance online with PsychoPy and Pavlovia. 

### CB 1 (Self-Paced)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb1")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb1")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow1 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

#### Extract cued responses CB1

```{r}
dataset1 <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="self-paced")

```

### CB 2 (Self-paced)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb2")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb2")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow2 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

#### Extract cued responses (CB2)
```{r}
dataset2 <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="self-paced")

```

### CB 1 (Timed) 

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb31")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb31")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow3 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```


#### Extract cued responses

```{r}
dataset3 <- datasetlow3 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="timed")

```

### CB 2 (Timed)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb32")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb32")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow4 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

#### Extract cued responses
```{r}
dataset4 <- datasetlow4 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="timed")

```

# Bind Data Cued Responses

```{r}
all<-rbind(dataset1, dataset2, dataset3, dataset4)

#write.csv(all, file="all.csv")

```

# JOls

Extract JOLs and combine them

```{r}

dataset1_jol <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="self-paced") %>% 
  na.omit(.) %>%
  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

dataset2_jol <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="self-paced") %>% 
  na.omit(.) %>%  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")


dataset3_jol <- datasetlow3 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="timed") %>% 
  na.omit(.) %>%
pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

dataset4_jol <- datasetlow4 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="timed") %>% 
  na.omit(.) %>%
  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

jol_all <- rbind(dataset1_jol, dataset2_jol, dataset3_jol, dataset4_jol)
```


# Scoring

The RD package scores cued response data. The data is loaded into a shiny application and then brought back in to R. The R code has some issues which is why we cant run it from here.

Next, we get the mean across all participants as a function of Typeface and Time on task. 

```{r}
setwd(here::here('TimeTaskSelf', "scored_recall")) # folder to find Ps in
recall_all<-read.csv(here::here('TimeTaskSelf', "scored_recall", "experiment3_times_recall80.csv"))  # path to data files


recall_all1 <- recall_all %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored)) %>%
  tidyr::pivot_wider(names_from="font", values_from="acc")

write.csv(recall_all1, file="wide_recall_timed.csv")

recall_all1 <- recall_all %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored))

write.csv(recall_all1, file="long_recall_timed.csv")


```
# Analysis

## Cued Recall

```{r}
#ANOVA


a1 <- aov_ez("id", "acc", recall_all1, 
            within=c("font"), between=c("cond")) # mixed

summary(a1)

aov=aov(acc ~ (font*cond) +
            Error(id/(font)), recall_all1)

a1

```
```{r}
aov_sum=report(aov)

aov_sum
```

```{r}
#ANOVA

a1 <- aov_ez("participant", "jols", jol_all, 
            within=c("Typeface"), between=c("cond")) # mixed

summary(a1)

aov=aov(jols ~ (Typeface*cond) +
            Error(participant/(Typeface)), jol_all)


```
```{r}

aov_sum <- report(aov)

aov_sum

```
# Plot 

## Cued recall

```{r,fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of Time on task for Experiment 3.", fig.height=4, fig.width=10, results="asis", eval=TRUE}

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

bold <- element_text(face = "bold", color = "black", size = 14) 

recall_all1 <- recall_all1 %>%
  mutate(Typeface=ifelse(font=="SF", "Sans Forgetica", "Arial")) %>%
  mutate(timed=ifelse(cond=="self-paced", "Self-paced", "Timed"))

means = recall_all1 %>%
  dplyr::group_by(timed, Typeface)%>% 
  dplyr::summarise(mean=mean(acc))


sfgen_wsci=summarySEwithin(data = recall_all1, measurevar = "acc",
                       withinvars = "Typeface", betweenvars = "timed", idvar = "id")

fig3a <- ggplot(recall_all1,aes(x=Typeface,y=acc,fill=Typeface))+ 
  facet_grid(~timed) + 
  geom_violinhalf(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = acc ),outlier.shape = NA,
               alpha = 0.5, width = .1, colour = "BLACK") +
    #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgen_wsci,aes(y=acc, group=1), size=1)+ 
  geom_pointrange2(data=sfgen_wsci, aes(y=acc, ymin=acc-ci, ymax=acc+ci), size=.5, color="red")+ 
  theme_cowplot() +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Porportion Correct on Final Test", x = "Typeface") + theme(legend.position = "none") + 
   geom_label_repel(data=sfgen_wsci, aes(y=acc, label=round(acc, 2)), min.segment.length = 0, seed = 42, box.padding = 0.5)
fig3a


```
## JOLS

```{r, fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of Time on task for Experiment 3.", fig.height=8, fig.width=10, results="asis"}

jol_rename <- jol_all %>%
  mutate(Typeface=ifelse(Typeface=="atypic_slider.response", "Sans Forgetica", "Arial")) %>%
  mutate(timed=ifelse(cond=="self-paced", "Self-paced", "Timed"))

means = jol_rename %>%
  dplyr::group_by(timed, Typeface)%>% 
  dplyr::summarise(mean=mean(jols))%>%
  dplyr::mutate(timed=as.factor(timed), Typeface=as.factor(Typeface))

# get withinsubject CIs
sfgenjol_wsci=summarySEwithin(data = jol_rename, measurevar = "jols",
                       withinvars = "Typeface", betweenvars = "timed", idvar = "participant")


fig3b <- ggplot(jol_rename,aes(x=Typeface,y=round(jols,2),fill=Typeface))+ 
  facet_grid(~timed) + 
  geom_violinhalf(position = position_nudge(x = .2, y = 0), alpha = .5,adjust=4)+
  #geom_violinhalf(fill_dots = "black") + 
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2, scale=width) +
  geom_boxplot(aes(x = Typeface, y = jols), outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
   #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgenjol_wsci,aes(y=jols, group=1), size=1)+ 
  geom_pointrange2(data=sfgenjol_wsci, aes(y=jols, ymin=jols-ci, ymax=jols+ci), size=.8, color="red")+ 
  theme_cowplot() +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Judgements of Learning", x = "Typeface") + theme(legend.position = "none") + 
   geom_label_repel(data=sfgenjol_wsci, aes(y=jols, label=round(jols, 2)), min.segment.length = 0, seed = 42, box.padding = 1)

fig3b


```

## Combine Plots

```{r fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of Time on task for Experiment 3.", fig.height=8, fig.width=6, results="asis", eval=TRUE}

fig3 <- plot_grid(
  fig3a, fig3b,
  labels = "AUTO", ncol= 1, nrow = 2
)

fig3

ggsave("fig3experiment3.png", width=10, height=12, dpi=500)
```




