---
title: "Expt2-HighvsLow"
author: "Jason Geller"
date: "12/29/2020"
output:
  html_document:
    df_print: paged
    toc: true
---

# Introduction

This RMD file comes from a preregistered study where we examined the moderating role of test expectancy on the Sans Forgetica effect/disfluency effect. We preregistered a sample size of 232 participants (116 in each group) through MTurk. This file explains how I read in the data, analyzed it, and plotted the results. If you have any questions please reach out to me at:jason.geller@ruccs.rutgers.edu

# Load Packages


```{r}
#packages you will need
library(tidyverse)
library(data.table)
library(here)
library(afex)
library(Rmisc)
library(cowplot)
library(see)
library(ggrepel)
library(report)
library(emmeans)
library(BayesFactor)

```
# Read in Raw Data

First we must read in data for each counterbalanced list. There were four and there was no simple way to counterbalance online with PsychoPy and Pavlovia. 
```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('Expt2_low_high', "mturk_cue_recall_low")) # folder to find Ps in

data=here::here("Expt2_low_high", "mturk_cue_recall_low")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow1 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

## CB 1 (Low Test Expectancy)

### Cued Recall Responses

```{r}
dataset1 <- datasetlow1 %>% 
    dplyr::group_by(participant, turkid)%>% # polygon_2 is a unqiue value for the test phase
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text)) %>% # some folks capitalzied words
  dplyr::mutate(cond="Low Test Expectancy", cb="low1") %>%
 dplyr::mutate(new_id=ifelse(is.na(participant)| participant=="J", turkid,participant)) #Mturkers used "me" for participant name so we need to extract unique id
as.data.frame(dplyr::count(dataset1, new_id))
```
### JOls

```{r}
dataset1_jol <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, atypic_slider.response, normal_slider.response) %>%
  mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  mutate(cond="Low Test Expectancy")%>%
  ungroup() %>%
  select(new_id1,  cond, atypic_slider.response, normal_slider.response) %>%
  na.omit(.)%>%
  tidyr::pivot_longer(atypic_slider.response:normal_slider.response, names_to = "TypeFace", values_to = "jols")

as.data.frame(dplyr::count(dataset1_jol, new_id1))
```

### RTs

```{r}

dataset1_rt <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, mouse_4.time, font) %>%
  dplyr::mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  dplyr::mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  dplyr::mutate(cond="Low Test Expectancy")%>%
  dplyr::ungroup() %>%
  dplyr::select(new_id1, cond, font, mouse_4.time)

as.data.frame(dplyr::count(dataset1_rt, new_id1))

```


## CB 2 - Low Test 

### Cued Recall

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('Expt2_low_high', "mturk_cue_recall_low2")) # folder to find Ps in

data=here::here("Expt2_low_high", "mturk_cue_recall_low2")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow2 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]}))
```

```{r}
dataset2 <- datasetlow2 %>% 
    dplyr::group_by(participant, turkid)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
  dplyr::mutate(textbox.text=tolower(textbox.text)) %>% 
  dplyr::mutate(cond="Low Test Expectancy", cb="low2") %>%
 dplyr::mutate(new_id=ifelse(is.na(participant),turkid,participant))
#Mturkers used "me" for participant name so we need to extract unique id
#check number of Ps in each CB and make sure names are unqiue 
as.data.frame(dplyr::count(dataset2, new_id))
```

### JOLs

```{r}
dataset2_jol <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, atypic_slider.response, normal_slider.response) %>%
  mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  mutate(cond="Low Test Expectancy")%>%
  ungroup() %>%
  select(new_id1,  cond, atypic_slider.response, normal_slider.response) %>%
  na.omit(.)%>%
  tidyr::pivot_longer(atypic_slider.response:normal_slider.response, names_to = "TypeFace", values_to = "jols")

as.data.frame(dplyr::count(dataset2_jol, new_id1))
```
### RTs

```{r}

dataset2_rt <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, mouse_4.time, font) %>%
  dplyr::mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  dplyr::mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  dplyr::mutate(cond="Low Test Expectancy")%>%
  dplyr::ungroup() %>%
  dplyr::select(new_id1, cond, font, mouse_4.time)

as.data.frame(dplyr::count(dataset2_rt, new_id1))

```

## CB 1 (High Test Expectancy)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('Expt2_low_high', "mturk_cue_recall_high")) # folder to find Ps in

data=here::here("Expt2_low_high", "mturk_cue_recall_high")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasethigh3 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:70]})) #fread makes reading in f
```


### Cued Responses

```{r }
dataset3 <- datasethigh3 %>% 
    dplyr::group_by(participant, turkid)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
  dplyr::mutate(textbox.text=tolower(textbox.text)) %>% 
  dplyr::mutate(cond="High Test Expectancy", cb="high1") %>%
 dplyr::mutate(new_id=ifelse(is.na(participant),turkid,participant))
#Mturkers used "me" for participant name so we need to extract unique id
#check number of Ps in each CB and make sure names are unqiue 
as.data.frame(dplyr::count(dataset2, new_id))
```

### JOLs

```{r}
dataset3_jol <- datasethigh3 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, atypic_slider.response, normal_slider.response) %>%
  mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  mutate(cond="High Test Expectancy")%>%
  ungroup() %>%
  select(new_id1,  cond, atypic_slider.response, normal_slider.response) %>%
  na.omit(.)%>%
  tidyr::pivot_longer(atypic_slider.response:normal_slider.response, names_to = "TypeFace", values_to = "jols")

as.data.frame(dplyr::count(dataset3_jol, new_id1))
```

### RTs
```{r}

dataset3_rt <- datasethigh3 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, mouse_4.time, font) %>%
  dplyr::mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  dplyr::mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  dplyr::mutate(cond="High Test Expectancy")%>%
  dplyr::ungroup() %>%
  dplyr::select(new_id1, cond, font, mouse_4.time)

as.data.frame(dplyr::count(dataset3_rt, new_id1))

```

## CB 2 (High Expectancy)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('Expt2_low_high', "mturk_cue_recall_high2")) # folder to find Ps in

data=here::here("Expt2_low_high", "mturk_cue_recall_high2")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasethigh4 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:70]})) #fread makes reading in f
```

### Cued Responses

```{r}
dataset4 <- datasethigh4 %>% 
    dplyr::group_by(participant, turkid)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
  dplyr::mutate(textbox.text=tolower(textbox.text)) %>% 
  dplyr::mutate(cond="High Test Expectancy", cb="high2") %>%
 dplyr::mutate(new_id=ifelse(is.na(participant),turkid,participant))
#Mturkers used "me" for participant name so we need to extract unique id
#check number of Ps in each CB and make sure names are unqiue 
as.data.frame(dplyr::count(dataset2, new_id))
```
### JOLs 

```{r}
dataset4_jol <- datasethigh4 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, atypic_slider.response, normal_slider.response) %>%
  mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  mutate(cond="High Test Expectancy")%>%
  ungroup() %>%
  select(new_id1,  cond, atypic_slider.response, normal_slider.response) %>%
  na.omit(.)%>%
  tidyr::pivot_longer(atypic_slider.response:normal_slider.response, names_to = "TypeFace", values_to = "jols")

as.data.frame(dplyr::count(dataset3_jol, new_id1))
```


### RTs


```{r}

dataset4_rt <- datasethigh4 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant,turkid, mouse_4.time, font) %>%
  dplyr::mutate(new_id=ifelse(is.na(participant), turkid, participant)) %>%
  dplyr::mutate(new_id1=ifelse(is.na(new_id), participant, new_id))%>%
  dplyr::mutate(cond="High Test Expectancy")%>%
  dplyr::ungroup() %>%
  dplyr::select(new_id1, cond, font, mouse_4.time)

as.data.frame(dplyr::count(dataset4_rt, new_id1))

```
 
 
# Combine High and Low CB lists
## Cued

```{r}
all_c<- rbind(dataset1, dataset2, dataset3, dataset4)

all_c %>% group_by(cb) %>% dplyr::summarise(count = n()) # make sure equal number of Ps in cbs


as.data.frame(dplyr::count(all_c, new_id))


#write.csv(all_c, file="test_expect.csv")

```

## JOLs

```{r}
all_jol <- rbind(dataset1_jol, dataset2_jol, dataset3_jol, dataset4_jol)
```

## RTs

```{r}
rt_all <- rbind(dataset1_rt, dataset2_rt, dataset3_rt, dataset4_rt)

rt_all1<- rt_all %>% 
  dplyr::group_by(new_id1, font, cond) %>% 
  dplyr::mutate(rt=mouse_4.time*1000) %>% 
dplyr::mutate(sdabove = mean(rt, na.rm=TRUE) +  2.5*sd(rt, na.rm=TRUE)) %>%
    dplyr::filter(rt > 150 || rt > sdabove) %>%
  dplyr::summarise(mean_rt= mean(log(rt), na.rm=TRUE)) %>%
   mutate(font=ifelse(font=="flu", "Arial", "Sans Forgetica")) %>%
  mutate(new_id1=ifelse(is.na(new_id1), "na1", new_id1)) %>%
  ungroup()

rt_all1
```

# Analysis

We employed 2 x 2 MIXED ANOVA. 

## Cued Recall

Read in data from the scored folder and aggregate (long and wide)

```{r}
setwd(here::here('Expt2_low_high', "Summary", "cued")) # folder to find Ps in

recall_highlow<-read.csv(here::here('Expt2_low_high', "Summary","cued", "Expt2_scored_recall.csv")) # folder to find Ps in)
```


```{r}
recall_highlow_agg_wide <- recall_highlow %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(Scored))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")

write.csv(recall_highlow_agg_wide, file="recall_expt2_summary.csv")


recall_highlow_agg <- recall_highlow %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::mutate(id=ifelse(is.na(id), "na1", id))%>%
  dplyr::summarise(mean_acc=mean(Scored))

write.csv(recall_highlow_agg, file="expt2_long_summary.csv")

  
```

```{r}
#ANOVA

a1 <- aov_ez("id", "mean_acc", recall_highlow_agg, 
            within=c("font"), between=c("cond")) # mixed

summary(a1)

a1





```

### Testing Interaction

```{r}
Within_Fitted_Interaction <- emmeans(a1, ~ font|cond)

Within_Fitted_Interaction

```

### Planned Comparisons

```{r}

pairs(Within_Fitted_Interaction) ## pairwise comparison with no correction

```

#### Effect sizes
```{r}
### get d_avg for high

recall_high <- recall_highlow %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(Scored))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")%>%
dplyr::filter(cond=="High Test Expectancy")%>%
  dplyr::ungroup() %>%
  summarise(mean1=mean(flu), sd1=sd(flu), mean2=mean(SF), sd2=sd(SF))

                   
                   


h=d.dep.t.avg(m1 = recall_high$mean1, m2 = recall_high$mean2, sd1 = recall_high$sd1,
                sd2 = recall_high$sd2, n = 116, a = .05)
  
  
#### get d_avg for low


recall_low <- recall_highlow %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(Scored))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")%>%
dplyr::filter(cond=="Low Test Expectancy")%>%
  ungroup() %>%
  summarise(mean1=mean(flu), sd1=sd(flu), mean2=mean(SF), sd2=sd(SF))


l=d.dep.t.avg(m1 = recall_low$mean1, m2 = recall_low$mean2, sd1 = recall_low$sd1,
                sd2 = recall_low$sd2, n = 116, a = .05)


h

l 

```


## JOLs

```{r}
#ANOVA

jol_a <- aov_ez("new_id1", "jols", all_jol, 
            within=c("TypeFace"), between=c("cond")) # mixed

summary(jol_a)
```

### Testing Interaction 
```{r}
Within_Fitted_Interaction <- emmeans(jol_a, ~ TypeFace|cond)

Within_Fitted_Interaction

```


### Effect Sizes

```{r}

recall_highjol <- all_jol %>% 
  dplyr::group_by(new_id1, TypeFace, cond) %>%
  dplyr::summarise(mean_jol=mean(jols))%>%
  tidyr::pivot_wider(names_from = "TypeFace", values_from = "mean_jol")%>%
dplyr::filter(cond=="High Test Expectancy")%>%
  ungroup() %>%
  summarise(mean1=mean(normal_slider.response ), sd1=sd(normal_slider.response), mean2=mean(atypic_slider.response ), sd2=sd(atypic_slider.response ))

h_jol=d.dep.t.avg(m1 = recall_highjol$mean1, m2 = recall_highjol$mean2, sd1 = recall_highjol$sd1,
                sd2 = recall_highjol$sd2, n = 116, a = .05)
  
recall_lowjol <- all_jol %>% 
  dplyr::group_by(new_id1, TypeFace, cond) %>%
  dplyr::summarise(mean_jol=mean(jols))%>%
  tidyr::pivot_wider(names_from = "TypeFace", values_from = "mean_jol")%>%
dplyr::filter(cond=="Low Test Expectancy")%>%
  ungroup() %>%
  summarise(mean1=mean(normal_slider.response ), sd1=sd(normal_slider.response), mean2=mean(atypic_slider.response ), sd2=sd(atypic_slider.response ))



l_jol=d.dep.t.avg(m1 = recall_lowjol$mean1, m2 = recall_lowjol$mean2, sd1 = recall_lowjol$sd1,
                sd2 = recall_lowjol$sd2, n = 115, a = .05)


```

```{r}

pairs(Within_Fitted_Interaction) ## pairwise comparison with no correction


```

## RTs

```{r}
#ANOVA

rt_a <- aov_ez("new_id1", "mean_rt",rt_all1, 
            within=c("font"), between=c("cond")) # mixed

summary(rt_a)

rt_a
```
#### Main Effects

No interaction, but main effect

```{r}
Within_font <- emmeans(rt_a, ~ font)

Within_font

Within_cond <- emmeans(rt_a, ~ cond)

Within_cond

```
### Bayesian Analyis

Main-effect vs. interaction model

```{r, eval=FALSE}

rt_all1$new_id1<-rep(1:232, each=2)

rt_all1$new_id1<-as.factor(rt_all1$new_id1)

rt_all1$cond<-as.factor(rt_all1$cond)

rt_all1$font<-as.factor(rt_all1$font)

bfrt = anovaBF(mean_rt ~ cond*font + new_id1, rt_all1, 
          whichRandom="new_id1")

#Bayes factor analysis
#--------------
#[1] font + cond + new_id1 : 4.322303 ±4.6%

##Against denominator:
#  mean_rt ~ font + cond + font:cond + new_id1 
#---
#Bayes factor type: BFlinearModel, JZS


```

# Plot

## Cued Recall


```{r}

library(see)
library(ggrepel)

#load in violin plot code
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

bold <- element_text(face = "bold", color = "black", size = 14) 

recall_highlow_agg <- recall_highlow_agg %>%
  dplyr::mutate(Typeface=ifelse(font=="SF", "Sans Forgetica", "Arial"))

#means by test and typeface 
means = recall_highlow_agg %>%
  dplyr::group_by(cond, Typeface)%>% 
  dplyr::summarise(mean=mean(mean_acc))

# get withinsub CIs
sfarial_wsci=summarySEwithin(data = recall_highlow_agg, measurevar = "mean_acc",
                       withinvars = "Typeface", betweenvars = "cond", idvar = "id")

recall_highlow_agg

```

```{r, fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of test expectancy for Experiment 2.", fig.height=8, fig.width=6, results="asis", eval=TRUE}

fig2a <- ggplot(recall_highlow_agg,aes(x=Typeface,y=mean_acc,fill=Typeface))+ 
  facet_grid(~cond) + 
  #geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = mean_acc ),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
    #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfarial_wsci,aes(y=mean_acc, group=1), size=1)+ 
  geom_pointrange(data=sfarial_wsci, aes(y=mean_acc, ymin=mean_acc-ci, ymax=mean_acc+ci), size=.3, color="red")+ 
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Porportion Correct on Final Test", x = "Typeface") + theme(legend.position = "none") + 
   geom_label_repel(data=sfarial_wsci, aes(y=mean_acc, label=round(mean_acc, 2)), min.segment.length = 0, seed = 42, box.padding = 0.8) + 
   theme_cowplot(font_size=14)+ 
  theme(legend.position = "none")


fig2a
```


## JOL

```{r, fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. JOLs as a function of testing expectancy in Experiment 2.", fig.height=8, fig.width=6, results="asis", eval=TRUE}

jol_rename <- all_jol %>%
  mutate(Typeface=ifelse(TypeFace=="atypic_slider.response", "Sans Forgetica", "Arial"))

means = jol_rename %>%
  dplyr::group_by(cond, Typeface)%>% 
  dplyr::summarise(mean=mean(jols))

# get withinsubject CIs
sfgenjol_wsci= Rmisc::summarySEwithin(data = jol_rename, measurevar = "jols",
                       withinvars = "Typeface", betweenvars = "cond", idvar = "new_id1")


fig2b <- ggplot(jol_rename,aes(x=Typeface,y=jols,fill=Typeface))+ 
  facet_grid(~cond) + 
  #geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = jols),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
   #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgenjol_wsci,aes(y=jols, group=1), size=1)+ 
  geom_pointrange(data=sfgenjol_wsci, aes(y=jols, ymin=jols-ci, ymax=jols+ci), size=.3, color="red")+ 
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Judgements of Learning", x = "Typeface") +  theme(legend.position = "none")+ 
  geom_label_repel(data=sfgenjol_wsci, aes(y=jols, label=round(jols, 2)), min.segment.length = 0, seed = 42, box.padding = 0.8) + 
  theme_cowplot(font_size=14)+ 
  theme(legend.position = "none")

fig2b
```

## RTs

```{r, fig.align="center", fig.height=8, fig.width=6, results="asis", eval=TRUE}

means = rt_all1 %>%
  dplyr::group_by(cond, font)%>% 
  dplyr::summarise(mean=mean(font))

# get withinsubject CIs
sfgenrt_wsci= Rmisc::summarySEwithin(data = rt_all1, measurevar = "mean_rt",
                       withinvars = "font", betweenvars = "cond", idvar = "new_id1")


fig2c <- ggplot(rt_all1,aes(x=font,y=mean_rt,fill=font))+ facet_grid(~cond) + 
  #geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = font , y = mean_rt),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
   #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgenrt_wsci,aes(y=mean_rt, group=1), size=1)+ 
  geom_pointrange(data=sfgenrt_wsci, aes(y=mean_rt, ymin=mean_rt-ci, ymax=mean_rt+ci),size=.3, color="red") + 
  scale_colour_brewer(palette = "lego")+
  scale_fill_brewer(palette = "lego") +
  labs(y = "log(RT/s)", x = "Typeface") + theme(legend.position = "none") + 
   geom_label_repel(data=sfgenrt_wsci, aes(y=mean_rt, label=round(mean_rt, 2)), min.segment.length = 0, seed = 42, box.padding = 0.5) + 
theme_cowplot(font_size=14) + 
  theme(legend.position = "none")



fig2c

```


# Combine Plots


```{r, fig.align="center", fig.height=16, fig.width=8, results="asis", eval=TRUE}

fig2 <- plot_grid(
  fig2a, fig2b, fig2c,
  labels = "AUTO", ncol= 1, nrow = 3
)

fig2

ggsave("figexpt2.png", width=8, height=12, dpi=500)

```