---
title: "Experiment 3: Time_on_task"
output:
  html_document:
    df_print: paged
    toc: true
---

# Introduction

In a preregistered study we manipulated the influence of time on task (Self-paced vs. Timed (3 s) on the Sans Forgetica effect/disfluency effect. We collected 232 participants (116 in each group) on Prolific. This file explains how to read in the data, analyze, and plot the results. 

# Read in Data

Load packages and read in data for counterbalance 1

```{r}
#packages you will need
library(tidyverse)
library(data.table)
library(here)
library(afex)
library(Rmisc)
library(cowplot)
library(see)
library(ggrepel)
#library(report)
library(emmeans)
library(BayesFactor)
library(MOTE)
```

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb1")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb1")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow1 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

Here we extract the cued responses
```{r cars}
dataset1 <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="self-paced")

```

Read in raw data for counterbalance 2 
```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb2")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb2")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow2 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

Extract the cued responses
```{r cars}
dataset2 <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="self-paced")

```

Read in the data for timed cb1 

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb31")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb31")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow3 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```


extract cued responses
```{r cars}
dataset3 <- datasetlow3 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="timed")

```
read in data for timed cb 2
```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb32")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb32")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow4 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

extract cued responses
```{r cars}
dataset4 <- datasetlow4 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="timed")

```

# Bind Data

Bind all the cued responses
```{r}
all<-rbind(dataset1, dataset2, dataset3, dataset4)

write.csv(all, file="all.csv")


```

#Scoring

The RD package scores cued response data. The data is loaded into a shiny application and then brought back in to R. The R code has some issues which is why we cant run it from here.

Next, we get the mean across all participants as a function of Typeface and Timed group. 

```{r}
setwd(here::here('TimeTaskSelf', "scored_recall")) # folder to find Ps in
recall_all<-read.csv(here::here('TimeTaskSelf', "scored_recall", "experiment3_times_recall80.csv"))  # path to data files


recall_all1 <- recall_all %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored)) %>%
  tidyr::pivot_wider(names_from="font", values_from="acc")

write.csv(recall_all1, file="wide_recall_timed.csv")

recall_all1 <- recall_all %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored))

write.csv(recall_all1, file="long_recall_timed.csv")


```
# Analysis

## Cued Recall

Run the  2 x 2 ANOVA analysis

```{r}
#ANOVA


a1 <- aov_ez("id", "acc", recall_all1, 
            within=c("font"), between=c("cond")) # mixed

summary(a1)



a1
```

# Main Effects

Get means for each main effect

```{r}
Within_font <- emmeans(a1, ~ font)

Within_font

Within_cond <- emmeans(a1, ~ cond)

Within_cond

```


### Interaction

```{r}
Within_Fitted_Interaction <- emmeans(a1, ~ font|cond)

Within_Fitted_Interaction

```


### Planned Comparisons

```{r}

pairs(Within_Fitted_Interaction) ## pairwise comparison with no correction

```
### Effect sizes

```{r}

recall_sp <- recall_all1 %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(acc))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")%>%
dplyr::filter(cond=="self-paced")%>%
  ungroup() %>%
  summarise(mean1=mean(flu), sd1=sd(flu), mean2=mean(SF), sd2=sd(SF))

sp_recall=d.dep.t.avg(m1 = recall_sp$mean1, m2 = recall_sp$mean2, sd1 = recall_sp$sd1,
                sd2 = recall_sp$sd2, n = 116, a = .05)
  
recall_timed <- recall_all1 %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(acc))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")%>%
dplyr::filter(cond=="timed")%>%
  ungroup() %>%
  summarise(mean1=mean(flu), sd1=sd(flu), mean2=mean(SF), sd2=sd(SF))

time_recall=d.dep.t.avg(m1 = recall_timed$mean1, m2 = recall_timed$mean2, sd1 = recall_timed$sd1,
                sd2 = recall_timed$sd2, n = 116, a = .05)
  
sp_recall
time_recall


```


### Bayesian Analyis

Run the 2 x 2 Bayesian Analyis
```{r}

recall_all1$new_id1<-rep(1:232, each=2)

recall_all1$new_id1<-as.factor(recall_all1$new_id1)

recall_all1$cond<-as.factor(recall_all1$cond)

recall_all1$font<-as.factor(recall_all1$font)


bfcue = anovaBF(acc ~ cond*font, recall_all1, 
          whichRandom="new_id1")


#Bayes factor analysis
--------------
#[1] font + cond : 5.497366 ±3.24%

#Against denominator:
#  acc ~ font + cond + font:cond 
#---
#Bayes factor type: BFlinearModel, JZS


```


# JOLs


Extract JOLs and combine them

```{r}

dataset1_jol <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="self-paced") %>% 
  na.omit(.) %>%
  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

dataset2_jol <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="self-paced") %>% 
  na.omit(.) %>%  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")


dataset3_jol <- datasetlow3 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="timed") %>% 
  na.omit(.) %>%
pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

dataset4_jol <- datasetlow4 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="timed") %>% 
  na.omit(.) %>%
  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

jol_all <- rbind(dataset1_jol, dataset2_jol, dataset3_jol, dataset4_jol)

jol_all_wide <- jol_all %>% 
  pivot_wider(names_from = "Typeface", values_from="jols")

#write.csv(jol_all_wide, file="expt3_jols_sum.csv")


```
## JOLs Analyis

A 2 x 2 Mixed ANOVA was run. 

```{r}
#ANOVA

a1 <- aov_ez("participant", "jols", jol_all, 
            within=c("Typeface"), between=c("cond")) # mixed

summary(a1)

a1
```
### Main Effects
```{r}
Within_font <- emmeans(a1, ~ Typeface)

Within_font

Within_cond <- emmeans(a1, ~ cond)

Within_cond

```




### Testing Interaction 
```{r}
Within_Fitted_Interaction <- emmeans(a1, ~ Typeface|cond)

Within_Fitted_Interaction

```
### Effect sizes

```{r}

recall_spjol <- jol_all %>% 
  dplyr::group_by(participant, Typeface, cond) %>%
  dplyr::summarise(mean_jol=mean(jols))%>%
  tidyr::pivot_wider(names_from = "Typeface", values_from = "mean_jol")%>%
dplyr::filter(cond=="self-paced")%>%
  ungroup() %>%
  summarise(mean1=mean(normal_slider.response ), sd1=sd(normal_slider.response), mean2=mean(atypic_slider.response ), sd2=sd(atypic_slider.response ))

sp_jol=d.dep.t.avg(m1 = recall_spjol$mean1, m2 = recall_spjol$mean2, sd1 = recall_spjol$sd1,
                sd2 = recall_spjol$sd2, n = 116, a = .05)
  
recall_timejol <- jol_all %>% 
  dplyr::group_by(participant, Typeface, cond) %>%
  dplyr::summarise(mean_jol=mean(jols))%>%
  tidyr::pivot_wider(names_from = "Typeface", values_from = "mean_jol")%>%
dplyr::filter(cond=="timed")%>%
  ungroup() %>%
  summarise(mean1=mean(normal_slider.response ), sd1=sd(normal_slider.response), mean2=mean(atypic_slider.response ), sd2=sd(atypic_slider.response ))



t_jol=d.dep.t.avg(m1 = recall_timejol$mean1, m2 = recall_timejol$mean2, sd1 = recall_timejol$sd1,
                sd2 = recall_timejol$sd2, n = 116, a = .05)
sp_jol
t_jol


```

# Bayesian Analysis 

```{r}

jol_all$new_id1<-rep(1:232, each=2)

jol_all$new_id1<-as.factor(jol_all$new_id1)

jol_all$cond<-as.factor(jol_all$cond)

jol_all$Typeface<-as.factor(jol_all$Typeface)


bftimed = anovaBF(jols ~ cond*Typeface, jol_all, 
          whichRandom="new_id1")

```


# Plot

## Cued Recall 


```{r}

library(see)
library(ggrepel)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

bold <- element_text(face = "bold", color = "black", size = 14) 

recall_all1 <- recall_all1 %>%
  mutate(Typeface=ifelse(font=="SF", "Sans Forgetica", "Arial")) %>%
  mutate(timed=ifelse(cond=="self-paced", "Self-paced", "Timed"))

means = recall_all1 %>%
  dplyr::group_by(timed, Typeface)%>% 
  dplyr::summarise(mean=mean(acc))


sfgen_wsci=summarySEwithin(data = recall_all1, measurevar = "acc",
                       withinvars = "Typeface", betweenvars = "timed", idvar = "id")

fig3a <- ggplot(recall_all1,aes(x=Typeface,y=acc,fill=Typeface))+ 
  facet_grid(~timed) + 
  #geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = acc ),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
    #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgen_wsci,aes(y=acc, group=1), size=1)+ 
  geom_pointrange(data=sfgen_wsci, aes(y=acc, ymin=acc-ci, ymax=acc+ci), size=.3, color="red")+ 
  theme_cowplot(font_size=14) +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Porportion Correct on Final Test", x = "Typeface") + theme(legend.position = "none") + 
   geom_label_repel(data=sfgen_wsci, aes(y=acc, label=round(acc, 2)), min.segment.length = 0, seed = 42, box.padding = 0.5)

fig3a

```

## JOLs

```{r}

jol_rename <- jol_all %>%
  mutate(Typeface=ifelse(Typeface=="atypic_slider.response", "Sans Forgetica", "Arial")) %>%
  mutate(timed=ifelse(cond=="self-paced", "Self-paced", "Timed"))

means = jol_rename %>%
  dplyr::group_by(timed, Typeface)%>% 
  dplyr::summarise(mean=mean(jols))

# get withinsubject CIs
sfgenjol_wsci=summarySEwithin(data = jol_rename, measurevar = "jols",
                       withinvars = "Typeface", betweenvars = "timed", idvar = "participant")



fig3b <- ggplot(jol_rename,aes(x=Typeface,y=jols,fill=Typeface))+ facet_grid(~timed) + 
 # geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = jols),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
   #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgenjol_wsci,aes(y=jols, group=1), size=1)+ 
  geom_pointrange(data=sfgenjol_wsci, aes(y=jols, ymin=jols-ci, ymax=jols+ci), size=.3, color="red")+ 
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Judgements of Learning", x = "Typeface") + theme(legend.position = "none") + 
   geom_label_repel(data=sfgenjol_wsci, aes(y=jols, label=round(jols, 2)), min.segment.length = 0, seed = 42, box.padding = 0.1) + 
  theme_cowplot(font_size=14) + 
  theme(legend.position = "none")

fig3b

```

## RTs

RTs were not analyzed as they were only collected in the self-paced condition. 

```{r, fig.align="center", fig.height=16, fig.width=8, results="asis", eval=TRUE}

fig3 <- plot_grid(
  fig3a, fig3b,
  labels = "AUTO", ncol= 1, nrow = 3
)

fig3

ggsave("figexpt2.png",width=10, height=12, dpi=500)

```





