---
title: "Experiment 3: Time_on_task"
output:
  html_document:
    df_print: paged
    toc: true
---

# Introduction

In a preregistered study we manipulated the influence of time on task (Self-paced vs. Timed (3 s) on the Sans Forgetica effect/disfluency effect. We collected 232 participants (116 in each group) on Prolific. This file explains how to read in the data, analyze, and plot the results. 

## Load in packages

```{r}
#packages you will need
library(tidyverse)
library(data.table)
library(here)
library(afex)
library(Rmisc)
library(cowplot)
library(patchwork)
library(see)
library(ggrepel)
library(report)
library(lrd)
library(emmeans)
library(MOTE)
library(BayesFactor)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R") # violin graph source code

```

## Read in Data

First we must read in data for each counterbalanced list. There were four and there was no simple way to counterbalance online with PsychoPy and Pavlovia. 

### CB 1 (Self-Paced)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb1")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb1")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow1 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

#### Extract cued responses CB1

```{r}
dataset1 <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="self-paced")

```

### CB 2 (Self-paced)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb2")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb2")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow2 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

#### Extract cued responses (CB2)
```{r}
dataset2 <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="self-paced")

```

### CB 1 (Timed) 

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb31")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb31")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow3 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```


#### Extract cued responses

```{r}
dataset3 <- datasetlow3 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="timed")

```

### CB 2 (Timed)

```{r message=FALSE, warning=FALSE, echo=FALSE} 
# read in low test expect data exported from gorilla
setwd(here::here('TimeTaskSelf', "cb32")) # folder to find Ps in

data=here::here('TimeTaskSelf', "cb32")  # path to data files

file_list=list.files(data, pattern=".csv") # list of data files
 
# read in all files
datasetlow4 <-
  do.call("rbind", lapply(file_list, FUN=function(files){
    
    for (i in 1:length(files)){ 
      if(file.exists(files[i])){
        message( "now processing:", files[i])
      }
    }
    fread(files, header=TRUE, sep=",", na.strings = "", fill=TRUE)[,1:60]})) #fread makes reading in f
```

#### Extract cued responses
```{r}
dataset4 <- datasetlow4 %>% 
    dplyr::group_by(participant)%>%
    dplyr::filter(mouse_5.clicked_name=="polygon_2") %>% dplyr::select(textbox.text, cue1, targ1, font) %>%
    mutate(textbox.text=tolower(textbox.text), acc=ifelse(textbox.text==cue1, 1, 0)) %>% 
  mutate(cond="timed")

```

# Combine Data 

## Cued Responses

```{r}
all<-rbind(dataset1, dataset2, dataset3, dataset4)

#write.csv(all, file="all.csv")

```

## JOls

Extract JOLs and combine them

```{r}

dataset1_jol <- datasetlow1 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="self-paced") %>% 
  na.omit(.) %>%
  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

dataset2_jol <- datasetlow2 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="self-paced") %>% 
  na.omit(.) %>%  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")


dataset3_jol <- datasetlow3 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="timed") %>% 
  na.omit(.) %>%
pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

dataset4_jol <- datasetlow4 %>% 
    dplyr::group_by(participant)%>%
     dplyr::select(participant, atypic_slider.response, normal_slider.response) %>%
  mutate(cond="timed") %>% 
  na.omit(.) %>%
  pivot_longer(atypic_slider.response:normal_slider.response, names_to = "Typeface", values_to = "jols")

jol_all <- rbind(dataset1_jol, dataset2_jol, dataset3_jol, dataset4_jol)
```

# Analysis

## Cued Recall

### Read in Scored file

Takes data from Shiny LRD package.

```{r message=FALSE, warning=FALSE, echo=FALSE}
setwd(here::here('TimeTaskSelf', "scored_recall")) # folder to find Ps in

recall_time<-read.csv(here::here('TimeTaskSelf', "scored_recall", "experiment3_times_recall80.csv"))  # path to data files

recall_all1_diff <- recall_time %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored)) %>%
  tidyr::pivot_wider(names_from="font", values_from="acc") %>%
  mutate(Difference=SF-flu, cond=ifelse(cond=="self-paced","Self-paced", "Timed(3s)"))

recall_all_mean <- recall_all1_diff %>% 
  dplyr::group_by(cond)%>%
  dplyr::summarise(mean=mean(Difference))

#write.csv(recall_all1, file="wide_recall_timed.csv")

recall_all1 <- recall_time %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored))

#write.csv(recall_all1, file="long_recall_timed.csv")



```


### Cued Response Scoring

The LRD package scores cued response data. The data is loaded into a shiny application and then brought back in to R. Below you can get proprotion correct by participant or the the trial-level Scored data, 

```{r, eval=FALSE}

#devtools::install_github("npm27/lrd") # load the package
#library(lrd)

all$textbox.text[is.na(all$textbox.text)] <- "" # does not work if NAs exists

all_c<-as.data.frame(all) # needs to be data frame

all_c$trial_id<-rep(1:5568) # needs to have unique rows for some reason 
# run lrd 
scored_cued = prop_correct_cued(all_c, 
                                responses = "textbox.text",
                                id = "participant",
                                id.trial = "trial_id",
                                key = "targ1", 
                                key.trial =  "trial_id",
                                cutoff = 3, 
                                group.by = c("font", "cond"))

recall_time<-scored_cued$DF_Participant # Prop by participant

recall_time<-scored_cued$Scored # trial-level (0,1)

```

### Difference

```{r}

recall_all1_diff <- recall_time %>% 
  dplyr::group_by(id, font, cond)%>% 
  dplyr::summarise(acc=mean(Scored)) %>%
  tidyr::pivot_wider(names_from="font", values_from="acc") %>%
  mutate(Difference=SF-flu, cond=ifelse(cond=="self-paced","Self-paced", "Timed(3s)"))

recall_all_mean <- recall_all1_diff %>% 
  dplyr::group_by(cond)%>%
  dplyr::summarise(mean=mean(Difference))

write.csv(recall_all1, file="wide_recall_timed.csv")


#write.csv(recall_all1, file="long_recall_timed.csv")



```

### ANOVA
```{r}
#ANOVA


a1 <- aov_ez("id", "acc", recall_all1, 
            within=c("font"), between=c("cond")) # mixed

a1

# Main Effects
```

### Main Effects

Get means for each main effect

```{r}
Within_font <- emmeans(a1, ~ font)
Within_font
Within_cond <- emmeans(a1, ~ cond)
Within_cond

```
### Interaction

```{r}
Within_Fitted_Interaction <- emmeans(a1, ~ font|cond)
Within_Fitted_Interaction

```

### Planned Comparisons

```{r}
pairs(Within_Fitted_Interaction) ## pairwise comparison with no correction

```
### Effect sizes

```{r}
recall_sp <- recall_all1 %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(acc))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")%>%
dplyr::filter(cond=="self-paced")%>%
  ungroup() %>%
  summarise(mean1=mean(flu), sd1=sd(flu), mean2=mean(SF), sd2=sd(SF))
sp_recall=d.dep.t.avg(m1 = recall_sp$mean1, m2 = recall_sp$mean2, sd1 = recall_sp$sd1,
                sd2 = recall_sp$sd2, n = 116, a = .05)
  
recall_timed <- recall_all1 %>% 
  dplyr::group_by(id, font, cond) %>%
  dplyr::summarise(mean_acc=mean(acc))%>%
  tidyr::pivot_wider(names_from = "font", values_from = "mean_acc")%>%
dplyr::filter(cond=="timed")%>%
  ungroup() %>%
  summarise(mean1=mean(flu), sd1=sd(flu), mean2=mean(SF), sd2=sd(SF))
time_recall=d.dep.t.avg(m1 = recall_timed$mean1, m2 = recall_timed$mean2, sd1 = recall_timed$sd1,
                sd2 = recall_timed$sd2, n = 116, a = .05)
  
sp_recall
time_recall
```

## Bayesian Analyis

### Cued Recall

Run the 2 x 2 Bayesian Analyis
```{r, eval=FALSE}

recall_all1$new_id<-rep(1:232, each=2)
recall_all1$new_id<-as.factor(recall_all1$new_id)
recall_all1$cond<-as.factor(recall_all1$cond)
recall_all1$font<-as.factor(recall_all1$font)

bfcue = anovaBF(acc ~ cond*font + new_id, recall_all1, 
          whichRandom=c("new_id"))
```

## JOLS

#### ANOVA

A 2 x 2 Mixed ANOVA was run. 

```{r}
#ANOVA
a1 <- aov_ez("participant", "jols", jol_all, 
            within=c("Typeface"), between=c("cond")) # mixed
summary(a1)
a1
```
### Main Effects
```{r}
Within_font <- emmeans(a1, ~ Typeface)
Within_font
Within_cond <- emmeans(a1, ~ cond)
Within_cond
```


### Testing Interaction 
```{r}
Within_Fitted_Interaction <- emmeans(a1, ~ Typeface|cond)
Within_Fitted_Interaction
```
### Effect sizes

```{r}
recall_spjol <- jol_all %>% 
  dplyr::group_by(participant, Typeface, cond) %>%
  dplyr::summarise(mean_jol=mean(jols))%>%
  tidyr::pivot_wider(names_from = "Typeface", values_from = "mean_jol")%>%
dplyr::filter(cond=="self-paced")%>%
  ungroup() %>%
  summarise(mean1=mean(normal_slider.response ), sd1=sd(normal_slider.response), mean2=mean(atypic_slider.response ), sd2=sd(atypic_slider.response ))
sp_jol=d.dep.t.avg(m1 = recall_spjol$mean1, m2 = recall_spjol$mean2, sd1 = recall_spjol$sd1,
                sd2 = recall_spjol$sd2, n = 116, a = .05)
  
recall_timejol <- jol_all %>% 
  dplyr::group_by(participant, Typeface, cond) %>%
  dplyr::summarise(mean_jol=mean(jols))%>%
  tidyr::pivot_wider(names_from = "Typeface", values_from = "mean_jol")%>%
dplyr::filter(cond=="timed")%>%
  ungroup() %>%
  summarise(mean1=mean(normal_slider.response ), sd1=sd(normal_slider.response), mean2=mean(atypic_slider.response ), sd2=sd(atypic_slider.response ))
t_jol=d.dep.t.avg(m1 = recall_timejol$mean1, m2 = recall_timejol$mean2, sd1 = recall_timejol$sd1,
                sd2 = recall_timejol$sd2, n = 116, a = .05)
sp_jol
t_jol
```

## Bayesian Analysis 

```{r}
jol_all$new_id1<-rep(1:232, each=2)
jol_all$new_id1<-as.factor(jol_all$new_id1)
jol_all$cond<-as.factor(jol_all$cond)
jol_all$Typeface<-as.factor(jol_all$Typeface)
bftimed = anovaBF(jols ~ cond*Typeface, jol_all, 
          whichRandom="new_id1")
```

# Plot 

## Cued recall

```{r,fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of Time on task for Experiment 3.", fig.height=4, fig.width=10, results="asis", eval=TRUE}


bold <- element_text(face = "bold", color = "black", size = 14) 

recall_all1 <- recall_all1 %>%
  mutate(Typeface=ifelse(font=="SF", "Sans Forgetica", ifelse(font=="flu", "Arial", "Difference"))) %>%
  mutate(timed=ifelse(cond=="self-paced", "Self-paced", "Timed"))

#means = recall_all1 %>%
 # dplyr::group_by(timed, Typeface)%>% 
 # dplyr::summarise(mean=mean(acc))


sfgen_wsci=summarySEwithin(data = recall_all1, measurevar = "acc",
                       withinvars = "Typeface", betweenvars = "timed", idvar = "id")

fig3a <- ggplot(recall_all1,aes(x=Typeface,y=acc,fill=Typeface))+ 
  facet_grid(~timed) + 
  #geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = acc ),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
    #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgen_wsci,aes(y=acc, group=1), size=1)+ 
  geom_pointrange(data=sfgen_wsci, aes(y=acc, ymin=acc, ymax=acc), size=.8, color="darkred")+ 
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Porportion Correct on Final Test", x = "Typeface") + 
  theme(legend.position = "none") + 
   geom_label_repel(data=sfgen_wsci, aes(y=acc, label=round(acc, 2)),seed = 42, box.padding = 0.8) + 
   theme_cowplot(font_size=14)+ 
  theme(legend.position = "none") +
  theme(axis.title = bold)

# plot difference plots 
fig3a_diff <- ggplot(recall_all1_diff,aes(x=cond,y=Difference, fill=cond)) + 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .18),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = cond, y = Difference),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
  stat_summary(fun.data="mean_cl_boot", colour="darkred", size=.8)+
  #geom_line(data=sfarial_wsci,aes(y=mean_acc, group=1), size=1)+ 
  #geom_pointrange(data=sfarial_wsci, aes(y=mean_acc, ymin=mean_acc-ci, ymax=mean_acc+ci), size=.5, color="red")+ 
  scale_colour_brewer(palette = "Accent")+
  scale_fill_brewer(palette = "Accent") +
  labs(y = "Test Difference (Sans Forgetica - Arial", x = "Time on Task")+
     theme_cowplot(font_size=14)+ 
  theme(legend.position = "none") +
  theme(axis.title =bold) + 
  geom_hline(yintercept = 0, linetype="dotted") + 
   geom_label_repel(data=recall_all_mean, aes(y=mean, label=round(mean, 2)), seed=42, box.padding=0.8)


fig3a
fig3a_diff


```


## JOLS

```{r, fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of Time on task for Experiment 3.", fig.height=8, fig.width=10, results="asis"}

jol_rename <- jol_all %>%
  mutate(Typeface=ifelse(Typeface=="atypic_slider.response", "Sans Forgetica", "Arial")) %>%
  mutate(timed=ifelse(cond=="self-paced", "Self-paced", "Timed"))


jol_diff <- jol_rename %>%
  pivot_wider(names_from="Typeface", values_from = "jols")%>%
  dplyr::mutate(Difference=`Sans Forgetica`- Arial) %>% 
  dplyr::mutate(cond=ifelse(cond=="self-paced", "Self-paced", "Timed(3s)"))

jol_diff_mean <- jol_diff %>% 
  dplyr::group_by(cond) %>% 
  dplyr::summarise(mean=mean(Difference))

means = jol_rename %>%
  dplyr::group_by(timed, Typeface)%>% 
  dplyr::summarise(mean=mean(jols))%>%
  dplyr::mutate(timed=as.factor(timed), Typeface=as.factor(Typeface))

# get withinsubject CIs
sfgenjol_wsci=summarySEwithin(data = jol_rename, measurevar = "jols",
                       withinvars = "Typeface", betweenvars = "timed", idvar = "participant")


fig3b <- ggplot(jol_rename,aes(x=Typeface,y=round(jols,2),fill=Typeface))+ 
  facet_grid(~timed) + 
  #geom_violinhalf(position = position_nudge(x = .2, y = 0), alpha = .5,adjust=4)+
  #geom_violinhalf(fill_dots = "black") + 
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = Typeface, y = jols ),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
   #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
  geom_line(data=sfgenjol_wsci,aes(y=jols, group=1), size=1)+ 
  geom_pointrange(data=sfgenjol_wsci, aes(y=jols, ymin=jols, ymax=jols), size=.8, color="darkred")+ 
  theme_cowplot() +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Judgements of Learning", x = "Typeface") + 
  theme(legend.position = "none") + 
   geom_label_repel(data=sfgenjol_wsci, aes(y=jols, label=round(jols, 2)),seed = 42, box.padding = 0.8) + 
  theme_cowplot(font_size=14)+ 
  theme(legend.position = "none") +
  theme(axis.title = bold)

  

fig3b_diff <- ggplot(jol_diff,aes(x=cond,y=Difference,fill=cond)) + 
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .4,adjust=4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.2) +
  geom_boxplot(aes(x = cond, y = Difference),outlier.shape = NA,
               alpha = 0.3, width = .1, colour = "BLACK") +
  stat_summary(fun.data="mean_cl_boot", colour="darkred", size=.8)+
   #stat_summary(fun="mean", geom="point", colour="darkred", size=3)+
 # geom_line(data=sfgenjol_wsci,aes(y=jols, group=1), size=1)+ 
 # geom_pointrange(data=sfgenjol_wsci, aes(y=jols, ymin=jols-ci, ymax=jols+ci), size=.3, color="red")+ 
  scale_colour_brewer(palette = "Accent")+
  scale_fill_brewer(palette = "Accent") +
  labs(y = "JOL Difference (Sans Forgetica - Arial)", x = "Time on Task") +  theme(legend.position = "none")+ 
  geom_label_repel(data=jol_diff_mean, aes(y=mean , label=round(mean, 2)), seed = 42, box.padding = 0.8) + 
   theme_cowplot(font_size=14)+ 
  theme(legend.position = "none") +
  geom_hline(yintercept = 0, linetype="dotted") + 
  theme(axis.title = bold)


fig3b

fig3b_diff


```

### Combine Plots

```{r fig.align="center", fig.cap="Raincloud plots (Allen et al., 2019) depicting raw data (dots), box plots, and half violin kernel desntiy plots, with mean (red dot) and within-participant 95 CIs. Cued recall accuracy as a function of Time on task for Experiment 3.", fig.height=8, fig.width=6, results="asis", eval=TRUE}

fig3 <- plot_grid(
  fig3a, fig3b,
  labels = "AUTO", ncol= 1, nrow = 2
)

ggsave("fig3experiment3.png", width=10, height=12, dpi=500)

fig3_diff <- plot_grid(fig3a_diff, fig3b_diff, ncol=, nrow=2)

ggsave("fig3_diff.png", width=10, height=12, dpi=500)


fig3_diff <- plot_grid(fig3a, fig3a_diff, fig3b, fig3b_diff, ncol=2, nrow=2)

ggsave("fig3_diff_all.png", width=12, height=14, dpi=500)

fig3_diff

```
